The non-independence of nations and why it matters

### 2022-12-21 manuscript.Rmd
add ethics statement

# Research Transparency and Reproducibility

All data and code to reproduce the statistical analyses in this manuscript can be found on the Open Science Framework: https://osf.io/uywx8/

>>>>

# Data Availability

All data can be found on the Open Science Framework: https://osf.io/uywx8/

# Code Availability

All code to reproduce the statistical analyses in this manuscript can be found on the Open Science Framework: https://osf.io/uywx8/

# Ethical Approval

Ethical approval was not required for the study as we analysed only secondary and simulated data.

### 2022-12-21 manuscript.tex
add ethics statement

\hypertarget{research-transparency-and-reproducibility}{%
\section{Research Transparency and Reproducibility}\label{research-transparency-and-reproducibility}}

All data and code to reproduce the statistical analyses in this manuscript can be found on the Open Science Framework: \url{https://osf.io/uywx8/}

>>>>

\hypertarget{data-availability}{%
\section{Data Availability}\label{data-availability}}

All data can be found on the Open Science Framework: \url{https://osf.io/uywx8/}

\hypertarget{code-availability}{%
\section{Code Availability}\label{code-availability}}

All code to reproduce the statistical analyses in this manuscript can be found on the Open Science Framework: \url{https://osf.io/uywx8/}

\hypertarget{ethical-approval}{%
\section{Ethical Approval}\label{ethical-approval}}

Ethical approval was not required for the study as we analysed only secondary and simulated data.
